The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-04-08 script/en/chapters/cryptomethods.tex
CT Book ed 12: Update of the bitcipher chapter, and many small typos like English '' instead of \glqq in German quotes.

The most well-known symmetric encryption procedure is the \index{DES} DES algorithm.
The DES algorithm has been developed by IBM in collaboration with the
National Security Agency \index{NSA} (NSA), and was published as a standard in
1975. Despite the fact that the procedure is relatively old, no effective attack
on it has yet been detected. The most effective way of attacking consists of
testing (almost) all possible keys until the right one is found ({\em brute-force-attack}).
\index{attack!brute-force} Due to the relatively short key length of
effectively 56 bits (64 bits, which however include 8 parity bits), numerous
messages encrypted using DES have in the past been broken. Therefore, the
procedure can not be considered secure any longer. Alternatives to the DES
procedure include IDEA\index{IDEA}, Triple-DES and especially AES.
\par \vskip + 3pt

Up-to-the-minute procedure is the symmetric AES standard\index{AES}. The associated
Rijndael algorithm was declared winner of the AES award on October 2nd, 2000
and thus succeeds the DES procedure.\index{AES}

>>>>

Before AES, the most well-known symmetric encryption procedure was the \index{DES} DES algorithm.
The DES algorithm has been developed by IBM in collaboration with the
National Security Agency \index{NSA} (NSA), and was published as a standard in
1975. Despite the fact that the procedure is relatively old, no effective attack
on it has yet been detected. The most effective way of attacking consists of
testing (almost) all possible keys until the right one is found ({\em brute-force-attack}).
\index{attack!brute-force} Due to the relatively short key length of
effectively 56 bits (64 bits, which however include 8 parity bits), numerous
messages encrypted using DES have in the past been broken. Therefore, the
procedure can not be considered secure any longer. Alternatives to the DES
procedure include IDEA\index{IDEA}, Triple-DES and especially AES.
\par \vskip + 3pt

Up-to-the-minute procedure for symmetric ciphers is the AES\index{AES}. The associated
Rijndael algorithm was declared winner of the AES award on October 2nd, 2000
and thus succeeds the DES procedure.\index{AES}

### 2016-04-08 script/en/chapters/introduction.tex
Corrected typos and overfull hbox; congruent index (no redundancy in wording; adjectives in lowercase in German; all normal words in lowercase in English)
CT Book ed 12: Added 3 graphics in primes.tex -- at the beginning and into section sieve of Eratosthenes. Started to search for a old /index problem [so later when solved the error detecting patterns ("\index{ZZZ") have to be taken off again.]
CT Book ed 12: Removed the \index debug code in the German version.
CT Book ed 12: Update of the bitcipher chapter, and many small typos like English '' instead of \glqq in German quotes.

% $Id$
% ............................................................................
%      V O R W O R T  und  E I N F U E H R U N G (Zusammenspiel CT-Buch und CT-Programmen) 
%      P R E F A C E  and  I N T R O D U C T I O N (Playing together of book and programs) 
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% --------------------------------------------------------------------------
\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Preface to the 12th Edition of the CrypTool Book xxxxxxxxxxxx}
\chapter*{Preface to the 12th Edition of the CrypTool Book xxxxxxxxxxxx}

@@

I hope that many readers have fun with this book and that they get 
out of it more interest and greater understanding of this modern but 
also very ancient topic.
\par \vskip + 15pt

\noindent Bernhard Esslinger
\\
\\
Frankfurt and Siegen (Germany), February 2016
\par \vskip + 30pt

\noindent PS:\\
We'd be glad if new authors would show up to add further chapters,
e.g. about\\
- the Riemann Zeta function,\\
- hash functions,\\
- lattice-based cryptography,\\
- random numbers, or\\
- the design and attack of crypto protocols (like SSL).

@@

Chapters \ref{Chapter_ModernCryptography} (Modern Cryptography),
\ref{Chapter_EllipticCurves} (Elliptic Curves), and
\ref{Chapter_HomomorphicCiphers} (Homomorphic Encryption)
require a deeper knowledge in mathematics, while the other chapters should
be understandable with a school leaving certificate.

@@

\noindent \textbf{The Pupil's Crypto Courses\index{Pupil's Crypto}}

@@

I am deeply grateful to all the people helping with their impressive
commitment who have made this global project so successful.
\par \vskip + 15pt

\noindent Bernhard Esslinger
\\
\\
Frankfurt/Siegen (Germany), February 2016

>>>>

% $Id$
% ............................................................................
%      V O R W O R T  und  E I N F U E H R U N G (Zusammenspiel CT-Buch und CT-Programme) 
%      P R E F A C E  and  I N T R O D U C T I O N (Playing together of book and programs)
%
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Preface to the 12th Edition of the CrypTool Book xxxxxxxxxxxx}
\chapter*{Preface to the 12th Edition of the CrypTool Book xxxxxxxxxxxx}

@@

I hope that many readers have fun with this book and that they get 
out of it more interest and greater understanding of this modern but 
also very ancient topic.

\par \vskip + 45pt
\noindent Bernhard Esslinger
\par \vskip + 10pt
\noindent Frankfurt/Siegen (Germany), April 2016

\par \vskip + 100pt
\noindent PS:\\
We'd be glad if new authors would show up to add further chapters,
e.g. about\\
- the Riemann Zeta function,\\
- hash functions,\\
- lattice-based cryptography,\\
- random numbers, or\\
- the design and attack of crypto protocols (like SSL).

@@

Chapters \ref{Chapter_ModernCryptography} (``Modern Cryptography''),
\ref{Chapter_EllipticCurves} (``\nameref{Chapter_EllipticCurves}''),
\ref{Chapter_BitCiphers} (``Bitblock and Bitstream Ciphers''), and % (``\nameref{Chapter_BitCiphers}'')
\ref{Chapter_HomomorphicCiphers} (``\nameref{Chapter_HomomorphicCiphers}'')
require a deeper knowledge in mathematics, while the other chapters should
be understandable with a school leaving certificate.

@@

\noindent \textbf{The Pupil's Crypto Courses\index{pupil's crypto}}

@@

I am deeply grateful to all the people helping with their impressive
commitment who have made this global project so successful.

\par \vskip + 45pt
\noindent Bernhard Esslinger
\par \vskip + 10pt
\noindent Frankfurt/Siegen (Germany), April 2016

### 2016-04-08 script/en/chapters/primes.tex
CT Book ed 12: Update of the bitcipher chapter, and many small typos like English '' instead of \glqq in German quotes.

Finding the first 10 digit prime in the decimal expansion of e is not easy,
but with various software tools, one can determine that the answer is
$$ 7,427,466,391 $$

>>>>

Finding the first 10 digit prime in the decimal expansion of $e$ is not easy,
but with various software tools, one can determine that the answer is
$$ 7,427,466,391 $$
